Rmarkdown Features

### 2018-07-08 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: "`r Sys.Date()`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
```

yaml Setup {.tabset}
-----------------------------

@@

### yaml of this Doc

@@

```yaml
---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: "`r Sys.Date()`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 3
    toc_float:
        collapsed: false
---
```

### HTML Output

@@

### PDF Output

@@

### PDF Output2
This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
```{yaml}
---
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
---
```

### PDF: header.tex{#pdf-header}

@@

### Bibliography

@@

knitr Parameters
--------------------------------

### Root
```r
knitr::opts_knit$set(root.dir='..')
```
The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default. In the case above, I changed it to  the **directory that is parent to the default directory**.

### Code Chunk & Figure Options
```r
library(svglite) 
knitr::opts_chunk$set(
	echo = FALSE, # No display code chunks
	message = FALSE,
	warning = FALSE,
	dev='svg', # or 'svglite' for multibite characters
	comment="",
	fig.dim = c(3.5, 3.5)  # (width, height)
)
options(digits = 2) # auto round to 2 decimals when printed
```

Dynamic Variables
-----------------------------

@@

$\LaTeX$ Math Rendering {.tabset}
-----------------------------
### Passing Matrix Object

#### Setup

@@

#### Include Matrix in Text

@@

### kable
```{r}
library(knitr)
library(dplyr)
iris_data <- head(iris) %>%
    select(Sepal.Length, Sepal.Width)

@@

### Plotting Expression
```{r fig.height=3}
library(latex2exp)
library(ggplot2)
iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
    select(Sepal.Length, Sepal.Width, Species)

@@

Display Code Chunk with Code Chunk
--------------------------------------------

@@

Bibliographies & Citations{#cite} 
-----------------------------------------

@@

### Citation syntax

#### Classical Citation: **Author**, **year**, and **brackets**
- `Some text [@Bib.ID].`
    - Some text [@RN9].

#### In-text Citation: **Author (year)**
- `@Bib.ID Some text`
    - @RN15 Some text

@@

#### Year only: Suppress Author
- `Some text [-@Bib.ID].`
    - Some text [-@RN9]

#### Two Citations
- `Some text [@Bib.ID1; @Bib.ID2].`
    -  Some text [@RN9; @RN15].

5. Prefix & Suffix
    - `Some text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
        -  Some text [see @RN9 pp. 45; also, @RN15 ch. 2].

### Include `.bib` file in Reference {.tabset}

@@

#### Reference heading

@@

#### Specific Refs
Include specific references that were **not cited** in the body of text.
```{pandoc}
---
nocite: |
  @item1, @item2
...
```

#### All Refs
Include **All references** in the body of text.
```{pandoc}
---
nocite: |
  @*
...
```

Emphasis {.tabset}
-----------------------------

### An Example

@@

### Colored divs

#### Bootstrap Alert

@@

#### Customized divs

@@

### Bootstrap Callouts

@@

````markdown
`r ''````{block2, type="bs-callout bs-callout-warning"}
#### Heading in Callout
**Calleout Text** texttexttexttexttexttext
```
````

```{block2, type="bs-callout bs-callout-warning"}
#### Heading in Callout
**Calleout Text** texttexttexttexttexttext
```

### New Line
```{markdown}
| Text of line 1
| Text of line 2

@@

### Attach Attributes
By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.

#### `class`

@@

#### Other Attributes
```{markdown}
Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
```

@@

Footnotes with Paragraphs
-----------------------------
Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.

@@

Shaped Images {.tabset}
-----------------------------

### Rounded Edge
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
```
![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
```
![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}

### Circle Image
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
```
![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}

#### Boostrap
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
```
![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}

### Thumbnail
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
```
![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}

@@

Figures
-----------------------------

### Captions
Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
```{r fig.cap='An Caption of the Plot'}
library(ggplot2)
ggplot(iris)+
    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
```

References
-----------------------------

>>>>

---
title: "Rmarkdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r Sys.Date()`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
str_date <- "`r Sys.Date()`"
```

# yaml Setup {.tabset}

@@

## yaml of this Doc {-}

@@

```yaml
---
title: "Rmarkdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r str_date`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---
```

## HTML Output {-}

@@

## PDF Output {-}

@@

## PDF Output2 {-}
This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
```{yaml}
---
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
---
```

## PDF: header.tex{- #pdf-header}

@@

## Bibliography {-}

@@

# knitr Parameters

## Root
```r
knitr::opts_knit$set(root.dir='..')
```
The root directory of the `.rmd` file you want to knit is set to the directory where the `.rmd` file is located by default. In the case above, I changed it to  the **directory that is parent to the default directory**. This is useful if you build websites with [R Markdown Websites](https://rmarkdown.rstudio.com/rmarkdown_websites.htm), since **R Markdown Websites** doesn't allow hierarchical website structure. By changing the root directory, you can more easly organize your project directory structure without violating the requirement of **R Markdown Websites**. This is especially true when you source a lot of Rscripts in the `.Rmd` files.

## Code Chunk & Figure Options
```r
library(svglite) 
knitr::opts_chunk$set(
	echo = FALSE, # No display code chunks
	message = FALSE,
	warning = FALSE,
	dev='svg', # or 'svglite' for multibite characters
	comment="",
	fig.dim = c(3.5, 3.5)  # (width, height)
)
options(digits = 2) # auto round to 2 decimals when printed
```

# Dynamic Variables

@@

# Some $\LaTeX$ for PDF output

- `\pagenumbering{gobble}`
This LaTeX code suppress the page number.

- `\pagenumbering{arabic}`
'Turn on' page number closed by `\pagenumbering{gobble}`.

- `\newpage`: Start a new page

The 3 type of code can be useful in the situation below:

```tex
---
title: "A Title"
author: "Someone"
date: "`r str_date`"
---

... Some content in the first page (title page) ...

\pagenumbering{gobble} % Suppress page number on the title page
\newpage               % Start a new page

... Some content in the second page ...

\pagenumbering{arabic} % Revert suppression of page number
                       % Now, the page num starts with '2'
```

# $\LaTeX$ Math {.tabset}

## Passing Matrix Object {-}

### Setup {-}

@@

### Include Matrix in Text {-}

@@

## kable {-}
```{r}
library(knitr)
library(dplyr)
iris_data <- head(iris) %>%
    select(Sepal.Length, Sepal.Width)

@@

## Plotting Expression {-}
```{r fig.height=3}
library(latex2exp)
library(ggplot2)
iris_data2 <- iris[c(1:3, 50:53, 100:103), ] %>%
    select(Sepal.Length, Sepal.Width, Species)

@@

# Display Code Chunk with Code Chunk

@@

# Bibliographies & Citations{#cite}

@@

## Citation syntax

### Classical Citation: **Author**, **year**, and **brackets** {-}
- `Some text [@Bib.ID].`
    - Some text [@RN9].

### In-text Citation: **Author (year)** {-}
- `@Bib.ID Some text`
    - @RN15 Some text

@@

### Year only: Suppress Author {-}
- `Some text [-@Bib.ID].`
    - Some text [-@RN9]

### Two Citations {-}
- `Some text [@Bib.ID1; @Bib.ID2].`
    -  Some text [@RN9; @RN15].

- Prefix & Suffix
    - `Some text [see @Bib.ID1 pp.45; also, @Bib.ID2 ch. 2].`
    -  Some text [see @RN9 pp. 45; also, @RN15 ch. 2].

## Include `.bib` file in Reference {.tabset}

@@

### Reference heading {-}

@@

### Specific Refs {-}
Include specific references that were **not cited** in the body of text.
```{pandoc}
---
nocite: |
  @item1, @item2
...
```

### All Refs {-}
Include **All references** in the body of text.
```{pandoc}
---
nocite: |
  @*
...
```

# Emphasis {.tabset}

## An Example {-}

@@

## Colored divs {-}

### Bootstrap Alert {-}

@@

### Customized divs {-}

@@

## Bootstrap Callouts {-}

@@

````markdown
`r ''````{block2, type="bs-callout bs-callout-warning"}
### Heading in Callout
**Calleout Text** texttexttexttexttexttext
```
````

```{block2, type="bs-callout bs-callout-warning"}
### Heading in Callout
**Calleout Text** texttexttexttexttexttext
```

## New Line {-}
```{markdown}
| Text of line 1
| Text of line 2

@@

## Attach Attributes {-}
By using `[`text`]`, pandoc turns the text in the square brackets into the HTML `<span>` tag. HTML `class`, `id`, attributes specific to `<span>` can then be attached by using the curly braces.

### `class` {-}

@@

### Other Attributes {-}
```{markdown}
Add color through [span style]{style="color:rgba(255, 0, 0, 1)"}
```

@@

# Footnotes with Paragraphs

Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.

@@

# Shaped Images {.tabset}

## Rounded Edge {-}
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
```
![](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}

### Boostrap {-}
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}
```
![Bootstrap Rounded](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-rounded}

## Circle Image {-}
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
```
![This is figure Caption](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}

### Boostrap {-}
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}
```
![Bootstrap Circle](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-circle}

## Thumbnail {-}
```{markdown}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}
```
![Bootstrap Thumbnail](/home/liao/local_depend/icons/libreoffice.ico){width=auto height="30%" .img-thumbnail}

@@

# Figures

## Captions

Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
````r
`r ''````{r fig.cap='An Caption of the Plot'}
library(ggplot2)
ggplot(iris) +
    geom_point(aes(x = Sepal.Length,
                   y = Sepal.Width,
                   color = Species)
               )
```
````

```{r echo=FALSE, fig.cap='An Caption of the Plot'}
library(ggplot2)
ggplot(iris)+
    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
```

# References
